---
title: “ETC5513 Assignment2”
authur: "Lulu Pi"
student ID: 27370038
output:
  html_document:
    df_print: paged
    theme: cerulean
    toc: yes
    toc_depth: '2'
  
---

# Introduction 
The goal of this report is to find when is the busy time of year to book a hotel room, and compare the average daily rate (ADR) within the 12 months in 2016 and between the city hotel and the resort hotel. 
The data used in this research contains booking information for a city hotel and a resort hotel in 2016, and includes information such as number of days that elapsed between the booking and arrival date, month of arrival date, ADR and number of special requests. 
This can help hotels to prepare the best services in advance on the most busy months, including the efficient supplies for special requests. Through comparing the ADR which shows how much revenue is made per room on average, therefore these hotels can make some decisions and look into ways to boost price per room to increase their ADR. 


# Loading libraries

```{r , message = FALSE}
library(tidyverse)
library(readr)
library(kableExtra)
library(ggplot2)
library(lubridate)
library(gridExtra)
library(rmdformats)
```

```{r, echo = TRUE, message = FALSE, warning = FALSE}
dat <- read_csv("Data/hotel_bookings.csv")
```

# The number of arrival in each month in 2016

# The average daily rate in 2016


# Conclusion


